---
title: "Assessment 3"
author: "Gessica Sardinha s4651724"
        "Oksana Kuchma s4661806"

date: "11/09/2021"
output: html_document
-------------------------
## Business report 
-------------------------

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
ikea_items <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-11-03/ikea.csv')

```

```{r}
library(tidyverse)
library(knitr)
library(tidymodels)
library(ggplot2)
```

# *DATA CLEANSING*

# I want to change the name of all the variables



```{r}
ikea_items <- ikea_items %>%
  rename("item_height" = height, "item_width" = width )
```



# 2. It is important to change the "character" variables into a "factor" for better analysis.



```{r}
ikea_items <- ikea_items %>%
  mutate_if(is.character, factor)
```


```{r}
  item_price <- cut_number(ikea_items$price, n = 3,labels=c("low", "med", "high"))
```


```{r}
ikea_items <- ikea_items%>%
  mutate(item_price = cut_number(ikea_items$price, n = 3,labels=c("low", "med", "high")))
```




# **ASKING QUESTION**

### For each of the 17 ikea items, we know their:


##### * experimental price of item group (item_price: either Med, Low, or High)

##### * size in milliliters at the start of the experiment (item_hight), and

##### * suture width at the end of the experiment (width).


##### **Major Question:** Can we predict the item_price of the ikea items by knowing their item_height and item_width?

##### **Subquestions:**

##### Q1. How many different types of *item_price* are there?

##### Q2. What is the relation between the *item_height* and the *item_width*?

##### Q3. Is the relation between the *item_height* and *item_width* dependent on *item_price*?

# **DESCRIPTIVE or EXPLORATORY ANALYSIS**

##### Now let's explore the data by finding the answer to the above subquestions.

### **Q1. How many different types of** item_price **are there?**

```{r}
ikea_items%>%
  count(item_price)%>%
  kable()

```



# We can see that there are only 3 types of  item_price - Med, Low & High. Each type has around 1230 values in it. This should make it easier for us to do our analysis and data viz.


# Q2. What is the relation between the *item_height* and the *item_width*?

## To find this relation, let's plot the item_height as X-axis and item_width as Y-axis. We then use the linear regression to see how they are related.

```{r}
ikea_items %>%
  ggplot(aes(item_height, item_width)) +
  geom_point() +
  geom_smooth(method = lm, se = FALSE)
```


## We can see that ikea_items that were larger in volume at the start of the experiment not tended to have wider sutures at the end. The slope of the line shows a positive relation between the item_height and theitem_height.


# Q3. Is the relation between the *item_height* and *item_width* dependent on *item_price*?

## Now, let's see if the above identified positive relation is dependent on the different size pattern - Item Price.

```{r}
ikea_items %>%
  ggplot(aes(item_height, item_width, colour = item_price)) +
  geom_point() +
  geom_smooth(method = lm, se = FALSE) +
   scale_color_viridis_d(option = "plasma", end = .7) +
  labs(x = "item_height", y = "item_height", colour = "Item Price")
```

## We can see that all the slopes shows a positive relation. However, these slopes look different. The ikea_items which are item High tend to become much more wider that those item Low. This means, the  width of the ikea_items are depended on their Item Price.

# **PREDICTIVE ANALYSIS**

## From our descriptive analysis, we have found that the final width of the urchins can be predicted by knowing their intial_volume and food_regime. We will now build a model to make these predictions.

# Step 1: Split the dataset into Training & Testing datasets.

```{r}
ikea_items_split <- initial_split(ikea_items)
ikea_items_train <- training(ikea_items_split)
ikea_items_test <- testing(ikea_items_split)
```

#Step 2: Pre-process the data.

##2.1 Set the recipe & get the ingredients 


```{r}
ikea_items_recipe <- recipe(price ~ item_height + item_width, data = ikea_items_train) 

summary(ikea_items_recipe)

```


## 2.2 Write the recipe steps

```{r}
ikea_items_recipe <- ikea_items_recipe %>%
  step_center(all_numeric(), -all_outcomes()) %>% 
  step_scale(all_numeric(), -all_outcomes()) %>% 
  step_corr(all_numeric())
```


## 2.3 Get ready with the prep

```{r}
ikea_items_prep <- prep(ikea_items_recipe, training = ikea_items_train)
```

## 2.4 Bake the recipe

```{r}
ikea_items_bake <- bake(ikea_items_prep, ikea_items_train)

ikea_items_bake
```


# Step 3: Build a model

## 3.1 Set up the model 

```{r}
model1 <- linear_reg() %>%
  set_mode("regression") %>%
  set_engine("lm")

model1
```

## 3.2 Fit the model

```{r}
model1_fitted <- model1 %>%
  fit(price ~ item_height * item_width, data = ikea_items_bake)

summary(model1_fitted)
```

## Step 4: Create a workflow


```{r}
workflow <- workflow() %>%
  add_recipe(ikea_items_recipe) %>%
  add_model(model1)
  
workflow
```



